Supplementary Figure 7

### 2018-05-15 inst/figure1d/figure1d.Rmd
updating all paths to figure numbers

<div class = "caption">
3’-RACE sequencing results displayed in the UCSC genome browser together with the annotated miR34a asRNA transcript (LINC01759) from GENCODE.
</div>

>>>>

<div class = "caption">
3’-RACE sequencing results displayed in the UCSC genome browser together with the annotated miR34a asRNA transcript (LINC01759) from Refseq
</div>

### 2018-05-15 inst/figure2a/figure2a.Rmd
updating all paths to figure numbers

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2a"][[1]])
ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 60,
   width = 53,
   units = "mm"
)
```

>>>>

#path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2a"][[1]])
#ggsave(
#   plot = figure,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 53,
#   units = "mm"
#)
```

### 2018-05-15 inst/figure3b/figure3b.Rmd
updating all paths to figure numbers

_Analysis_
The cell cycle phases ModFit software (Verity Software House) was used to quantify the percentage of cells in each cell cycle phase. Percentages were converted to log2 fractions for each sample. Student's t-test was used for statistical analysis comparing the mock vs miR34a asRNA overespression conditions using five (PC3) or three (Skov3) independant experiments.

@@

<div class="caption">
Cell cycle analysis in miR34a asRNA over-expressing PC3, Skov3, and Saos2 stable cell lines compared to their respective mock control. The points represent the values obtained from each independant experiment (PC3 n = 5; Skov3 n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

>>>>

_Analysis_

The cell cycle phases ModFit software (Verity Software House) was used to quantify the percentage of cells in each cell cycle phase. Percentages were converted to log2 fractions for each sample. Student's t-test was used for statistical analysis comparing the mock vs miR34a asRNA overespression conditions using five (PC3) or three (Skov3) independant experiments.

@@

<div class="caption">
Cell cycle analysis in miR34a asRNA over-expressing PC3, Skov3, and Saos2 stable cell lines compared to their respective mock control. The points represent the values obtained from each independant experiment (PC3 n = 5; Skov3 n = 3). 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

### 2018-05-15 inst/supp_figure1a/supp_figure1a.Rmd
updating all paths to figure numbers

---
title: "Figure 1-Supplement 1a"
subtitle: "TCGA correlation table"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

```{r, warning = FALSE}
url <- fileMap(type = "rds")["Figure 1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

>>>>

---
title: "Supplementary Figure 1a"
subtitle: "TCGA correlation table"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

```{r, warning = FALSE}

data <- getData("Supplementary Figure 1a")

### 2018-05-15 inst/supp_figure2d/supp_figure2d.Rmd
updating all paths to figure numbers

---
title: "Figure 1-Supplement 2e"
subtitle: "miR34a asRNA cellular localization"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

url <- fileMap(type = "rds")["Figure 1-Supplement 2e"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

>>>>

---
title: "Supplementary Figure 2d"
subtitle: "miR34a asRNA cellular localization"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

data <- getData("Supplementary Figure 2d")

### 2018-05-15 inst/supp_figure2e/supp_figure2e.Rmd
updating all paths to figure numbers

---
title: "Figure 1-Supplement 2d"
subtitle: "miR34a asRNA coding potential via CPC"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

url <- fileMap(type = "rds")["Figure 1-Supplement 2d"][[1]]
cpat <- read_rds(url(file.path(dataUrl, url)))
cpat

>>>>

---
title: "Supplementary Figure 2e"
subtitle: "miR34a asRNA coding potential via CPC"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

cpat <- getData("Supplementary Figure 2e")
cpat

### 2018-05-15 inst/supp_figure3c/supp_figure3c.Rmd
updating all paths to figure numbers

---
title: "Figure 2-Supplement 2"
subtitle: "P1 shRenilla HEK293t transfections"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    code_folding: hide
    theme: flatly
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
editor_options: 
  chunk_output_type: console
---

@@

url <- fileMap(type = "rds")["Figure 2-Supplement 2"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

>>>>

---
title: "Supplementary Figure 3c"
subtitle: "P1 shRenilla HEK293t transfections"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    code_folding: hide
    theme: flatly
vignette: |
  %\VignetteIndexEntry{Vignette Title} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
editor_options: 
  chunk_output_type: console
---

@@

data <- getData("Supplementary Figure 3c")

### 2018-05-15 inst/supp_figure7/supp_figure7.Rmd
updating all paths to figure numbers

#### _Conclusions_
Multiple splice junctions correspond to the miR34a asRNA transcrips and its isoforms (**Supplementary Fig 1d.**) with those being the most highly expressed corresponding to the annotated miR34a asRNA transcript. Despite this, no splice junctions appear to correspond to the intron in the lnc34a transcript. This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as claimed by the authors. An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected. Finally, lnc34a may not be expressed in any of the cell lines examined.

>>>>

#### _Conclusions_
Multiple splice junctions correspond to the miR34a asRNA transcrips and its isoforms (**Supplementary Fig 2c.**) with those being the most highly expressed corresponding to the annotated miR34a asRNA transcript. Despite this, no splice junctions appear to correspond to the intron in the lnc34a transcript. This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as claimed by the authors. An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected. Finally, lnc34a may not be expressed in any of the cell lines examined.
